\documentclass[11pt,fullpage]{article}
\usepackage{times}
\usepackage{fullpage}
\usepackage{natbib}
\usepackage{array}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{rotating} 
\usepackage{amsmath,amsthm,amssymb,epsf,graphics,algorithm,latexsym,times}
\usepackage{covington}
\usepackage{xspace,url}
\usepackage{subscript}
\usepackage{pdfpages}
\usepackage[bf,small]{caption}

	\addtolength{\topmargin}{-.25in}
	\addtolength{\textheight}{.75in}


\newcommand{\newcite}[1]{\citet{#1}}
\newcommand{\mc}{\multicolumn}
\newcommand{\rhcomment}[1]{{\bf [#1 -{\sc rh}]}}

\begin{document}

\newpage
\setcounter{page}{1}


\section*{Biographical Sketch: Chris Callison-Burch}


\subsubsection*{Professional Preparation}


\begin{tabular}{llll}
 Stanford University	& B.S.	& 2000	& Symbolic Systems Program \\
  University of Edinburgh	& M.S. &	2002 &	Computer Science\\
 University of Edinburgh & Ph.D.	&2008&	Informatics\\
\end{tabular}



\subsubsection*{Appointments}
\begin{itemize}
\item 2013-present: Aravind K. Joshi Term Assistant Professor,  University of Pennsylvania, Department of Computer and Information Science
\item 2010-2013: Associate Research Professor, Johns Hopkins University, Computer Science Department
\item 2007-2010: Assistant Research Professor, Johns Hopkins University, Computer Science Department
\end{itemize}



\subsubsection*{Products: Five Publications Most Closely Related to Proposed Research)}
%\subsubsection*{5 Most Cited Publications (statics from ACL Anthology Network and Google Scholar) }
%\noindent
%{\sf Publications and citation statistics available online at \url{http://clair.si.umich.edu/clair/anthology/}


\begin{enumerate}
\item C. Callison-Burch and M. Dredze (2010). Creating Speech and Language Data With Amazon's Mechanical Turk. \newblock In Proceedings of NAACL 2010 Workshop on Creating Speech and Language Data With Amazon's Mechanical Turk.   {\em 163 citations}

\item  C. Callison-Burch (2009).  Fast, Cheap, and Creative: Evaluating Translation Quality Using Amazon's Mechanical Turk. \newblock In Proceedings of EMNLP 2009. {\em 254 citations}


\item O. Zaidan and C. Callison-Burch (2011). Crowdsourcing Translation: Professional Quality from Non-Professionals. \newblock In Proceedings of ACL 2011.  {\em 116 citations}


\item S. Novotney and C. Callison-Burch (2010).  Cheap, Fast and Good Enough: Automatic Speech Recognition with Non-Expert Transcription. \newblock In Proceedings of NAACL 2010.   {\em 82 citations}


\item E. Pavlick, M. Post, D. Kachaev, A. Irvine and C. Callison-Burch (2014). The language Demographics of Amazon Mechanical Turk. \newblock In Proceedings of TACL 2014.    %{\em 14 citations}

\end{enumerate}


\subsubsection*{Five Other Publications (Most Cited Publications out of 80+ Total Publications) }
\noindent
\begin{enumerate}
\item P. Koehn, H. Hoang, A. Birch, C. Callison-Burch, M. Federico, N. Bertoldi, B. Cowan, W. Shen, C. Moran, R. Zens, C. Dyer, O. Bojar, A. Constantin, E. Herbst \newblock {\em Moses: Open Source Toolkit for Statistical Machine Translation.} \newblock In Proceedings of ACL-2007.  {\em 2,477 citations -- This is in the top 10 most cited papers out of the 23,000+ computational linguistics papers in the ACL Anthology Network}.

\item C. Callison-Burch, M. Osborne and P. Koehn. \newblock {\em Re-evaluating the Role of Bleu in Machine Translation Research.}  \newblock In Proceedings of EACL-2006.    {\em 387 citations}

\item C. Bannard and C. Callison-Burch \newblock {\em Paraphrasing With Bilingual Parallel Corpora.} \newblock In Proceedings of ACL-2005.  
  {\em 340 citations}

\item
C. Callison-Burch,  P. Koehn  and M. Osborne. \newblock {\em Improved Statistical Machine Translation Using Paraphrases.}  \newblock In Proceedings of HLT-NAACL-2006.     {\em 211 citations}


\item 
C. Callison-Burch, C. Fordyce, P. Koehn, C. Monz and J. Schroeder,  \newblock {\em Further Meta-Evaluation of Machine Translation.}  \newblock In Proceedings of ACL-2008 Workshop on Statistical Machine Translation. 
  {\em 197 citations}


\end{enumerate}

\subsubsection*{Other Activities}
%A list of up to five examples that demonstrate the broader impact of the individual’s professional and scholarly activities that focuses on the integration and transfer of knowledge as well as its creation. Examples could include, among others: innovations in teaching and training (e.g., development of curricular materials and pedagogical methods); contributions to the science of learning; development and/or refinement of research tools; computation methodologies, and algorithms for problem-solving; development of databases to support research and education; broadening the participation of groups underrepresented in science, mathematics, engineering and technology; and service to the scientific and engineering community outside of the individual’s immediate organization.
\begin{enumerate}
\item Innovations in teaching and training: I  created an undergraduate course on Crowdsourcing and Human Computation (http://crowdsourcing-class.org)
\item Innovations in teaching and training: I  co-created a project based course on Machine Translation.  Our pedagogical strategy was published in the journal Transaction of the ACL.
\item Service to the scientific community: I co-organized the Workshop on Statistical Machine Translation (WMT) and its shared tasks for 6 years.
\item Service to the scientific community: I was the Chairman of the North American chapter of the Association for Computational Linguistics (NAACL) drom 2011-2013
\end{enumerate}

%\vspace{-.33cm}
%\subsubsection*{Synergistic Activities}
%The PI has a 1 year subcontract for BBN examining the use of Mechanical Turk to classify and translate Arabic dialect data.   Google has given the PI a \$25,000 gift which will contribute towards creating data for this proposal.  Microsoft Research has promised an additional \$20,000.  The HLTCOE funded the pilot study on crowdsourcing translation described in the proposal.  None of these sources provide funding for the two graduate students, which are the bulk of the proposed budget.




  

\vspace{-.331cm}
\subsubsection*{Graduate Students and Fellows Supervised}
1st year PhD student: Anne Cocos\\
3rd year PhD student: Ellie Pavlick\\
Senior  PhD students: Juri Ganitkevitch, Courtney Napoles,  Jonny Weese\\
Postdoc: Wei Xu\\
Completed MS students: Alexandra Birch, Wren Thornton, Tsz Ping Chan, Luke Orland, Ryan Cotterell, Rui Yan\\
Completed PhD students: Lane Schwartz, Omar Zaidan, Xuchen Yao, Ann Irvine\\
Former Postdocs: Alex Klementiev, Matt Post
\noindent

\vspace{-.331cm}
\paragraph{Graduate Advisors}
Miles Osborne, 
Mark Steedman, 
Philipp Koehn

\bibliographystyle{apalike}
	

\end{document}






